Automated troubleshooting toolset for SDNs

### 2013-10-27 draft.tex

\begin{figure}
\centering
\includegraphics[scale=0.65]{layers.png}
\label{layers}
\caption{SDN architecture\protect\footnotemark}
\end{figure}
\footnotetext{Source : \cite{Heller:2013:LSL:2491185.2491197}}
\section{Network Troubleshooting - Tools}
\label{Network Troubleshooting - Tools}
\subsection{Network Debugger (NDB)}

\subsection{VeriFlow}
If the actual behavior of the network does not correspond to the policy, then the issue can potentially be found in the erroneous correspondance between the \textit{device state layer} and the \textit{policy layer}. There exist different tools to verify this hypothesis. The one we discuss here have the advantage to verify some network invariants in real-time. Other tools as Anteater and Header Space Analysis (HSA) that are also used in the same purpose carry out the static analysis of snapshots of the network data-plane state\cite{Kazemian:2012:HSA:2228298.2228311}\cite{Mai:2011:DDP:2018436.2018470}. Since SDN controllers are capable of installing around 30.000 flows per second while maintaining less than 10 ms delay for the installation, it is absolutely not enough to have tools that check for network invariant with a latency of the order of seconds \cite{Khurshid:2013:VVN:2482626.2482630}.\\
VeriFlow acts as a proxy in between the SDN controller and the switches and this proxy verifies some common network invariants at each forwarding rule installation with a very high speed. In order to achieve a 7ms delay inflation with regards to traditional TCP connections\footnote{Test configuration : 20 nodes OpenFlow network sing Mininet and a NOX controller\cite{Khurshid:2013:VVN:2482626.2482630} }, VeriFlow slices the network into equivalences classes, then builds a virtual forwarding graph for each ones using a trie structure, and finally checks invariants by traversing those graph with a depth-first search approach. Note that VeriFlow allows to spotting network issues before they reach the network, which is very valuable.\\
As limitations, we can note that presently, VeriFlow only checks for reachability invariants, and that it is not suitable for multiple/distributed controller \cite{Khurshid:2013:VVN:2482626.2482630}.

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.65]{layers.png}
\label{layers}
\caption{SDN architecture\protect\footnotemark}
\end{figure}
\footnotetext{Source : \cite{Heller:2013:LSL:2491185.2491197}}
\section{Network Troubleshooting - Tools}
\label{Network Troubleshooting - Tools}
\subsection{Network Debugger (NDB)}
SDNs bring a new way of building networks, like a programmer build a software, a network administrator will be able to program its network. The software programmer has tools to debug its program, like the well-known \textbf{gdb}.\\
\textbf{ndb} is a tool inspired from \textbf{gdb}, it aims at finding network error by identifying uncorrect sequence of events. \textbf{ndb} has the ability to do a sort of \textit{breakpoint}, which is in fact a packet filter. When packet are matched by this filter, the breakpoint is triggered and the entire trace of that packet is displayed. The authors mention that the term \textit{tracepoint} should be more appropriate but the term \textit{breakpoint} is more familiar. \textbf{ndb} uses its \textit{backtrace} primitive to show the sequence of events for a packet. This trace is simply the sequence of forwarding actions applied on the packet by the switches through which it passed. For example of \textbf{ndb} utilisation, please refer to its paper \cite{ndb paper}.\\
In our layering SDN architecture, \textbf{ndb} give us the opportunity to build a tool to confirm the right action of the policies implemented in the control application. For example, if a routing bug occurs in the network, a tool of top of \textbf{ndb} could observe paths taken by packets and complete switches states in order to conclude if the policies are correctly matched or not. If the policies are correctely matched, it means that the network administrator has written policies that dont't fit his needs. In this case, \textbf{ndb} has found the \textit{code layer} where the issue happen. Now if the policies are not correctly matched, then the issue does not come from an uncorrect implementation. \textbf{ndb} has thus exclude the implementation to be the root of the bug and the search can continue among other layers, with other tools such as \textbf{SOFT}\cite{SOFT paper}.
\subsection{VeriFlow}
If the actual behavior of the network does not correspond to the policy, then the issue can potentially be found in the erroneous correspondance between the \textit{device state layer} and the \textit{policy layer}. There exist different tools to verify this hypothesis. The one we discuss here have the advantage to verify some network invariants in real-time. Other tools as Anteater and Header Space Analysis (HSA) that are also used in the same purpose carry out the static analysis of snapshots of the network data-plane state\cite{Kazemian:2012:HSA:2228298.2228311}\cite{Mai:2011:DDP:2018436.2018470}. Since SDN controllers are capable of installing around 30.000 flows per second while maintaining less than 10 ms delay for the installation, it is absolutely not enough to have tools that check for network invariant with a latency of the order of seconds \cite{Khurshid:2013:VVN:2482626.2482630}.\\
VeriFlow acts as a proxy in between the SDN controller and the switches and this proxy verifies some common network invariants at each forwarding rule installation with a very high speed. In order to achieve a 7ms delay inflation with regards to traditional TCP connections\footnote{Test configuration : 20 nodes OpenFlow network sing Mininet and a NOX controller\cite{Khurshid:2013:VVN:2482626.2482630} }, VeriFlow slices the network into equivalences classes, then builds a virtual forwarding graph for each ones using a trie structure, and finally checks invariants by traversing those graph with a depth-first search approach. Note that VeriFlow allows to spotting network issues before they reach the network, which is very valuable.\\
As limitations, we can note that presently, VeriFlow only checks for reachability invariants, and that it is not suitable for multiple/distributed controller \cite{Khurshid:2013:VVN:2482626.2482630}.
